---
title: "decontam-ctd-18S-metazoan"
author: "Nina Yang, Postdoctoral Investigator, WHOI"
created date: "2023-05-26"
output: "2024-12-05"
last updated: null
---

## Background
This document outlines the stephyseq taken to decontaminate 18S V9 metabarcoding results from samples collected via CTD from the AR43 Cruise (Armstrong, March 2020) using the decontam package in R. The resulting project is a decontaminated phyloseq objective for protists only.

```{r install-pkgs, include=FALSE}

if (!requireNamespace("devtools", quietly = TRUE))
  {install.packages("devtools")};
if(!requireNamespace("BiocManager", quietly = TRUE))
  install.packages("BiocManager");
devtools::install_github("r-lib/conflicted");
BiocManager::install("tidyverse", force = TRUE); 
devtools::install_github("jbisanz/qiime2R", force = TRUE);
BiocManager::install("patchwork", force = TRUE); 
BiocManager::install("phyloseq", force = TRUE);
BiocManager::install("DT", force = TRUE); 
BiocManager::install("decontam", force = TRUE); 

```

```{r load-pkgs, include=FALSE}

library("conflicted"); packageVersion("conflicted")
library("tidyverse"); packageVersion("tidyverse")
library("qiime2R"); packageVersion("qiime2R")
library("patchwork"); packageVersion("patchwork")
library("phyloseq"); packageVersion("phyloseq")
library("DT"); packageVersion("DT")
library("decontam"); packageVersion("decontam")

```

## Identify Contaminants 

Samples will be decontaminated using the 'decontam' package on outputs processed in QIIME 2 

This was done using the "prevalence" method following the decontam tutorial: 
httphyseq:/benjjneb.github.io/decontam/vignettes/decontam_intro.html

The details of the QIIME 2 stephyseq were performed on WHOI's HPC (Poseidon) and outlined here:[INSERT LINK TO NOTES].

```{r import-files-met, eval = TRUE, message = FALSE, warning = FALSE}

# input QIIME 2 outputs

## sequence table
ASVs <- read_qza("../00_qiime2-outputs/18S/prdb-metazoa-ctd-table.qza")
names(ASVs)
ASVs$data[1:5,1:5]  #show first 5 samples and first 5 taxa

## updated metadata
metadata <- read.table("18S/metadata_AR43_update_ctd.txt", sep='\t', header=T, row.names=1, comment = "")

head(metadata)
tail(metadata)
metadata <- metadata %>% select(-c(duration))
head(metadata)
tail(metadata)
colnames(metadata)

## taxonomy
taxonomy <- read_qza("../00_qiime2-outputs/18S/ar43-18s-silvadb-taxonomy_hybrid_classify.qza")
head(taxonomy$data)
strsplit_output <- (strsplit(as.character(taxonomy$data$Taxon), ";"))
max_length <- max(lengths(strsplit_output))

list_of_vectors <- lapply(strsplit_output, function(x) {
  c(x, rep(NA, max_length - length(x)))
})

head(list_of_vectors)

tax_table <- do.call(rbind, list_of_vectors)
colnames(tax_table) <- c("Domain", "Kingdom", "Phylum", "Class", "Order", "Family", "Genus", "Species")

head(tax_table)
rownames(tax_table) <- taxonomy$data$Feature.ID
tax_table[is.na(tax_table)] <- "Unassigned"
head(tax_table)

physeq <- phyloseq(
  otu_table(ASVs$data, taxa_are_rows = T),
  tax_table(tax_table),
  sample_data(metadata)
)

physeq # check that this is a phyloseq object
rank_names(physeq, errorIfNULL = TRUE)
class(physeq)

datatable(sample_data(physeq))
head(sample_data(physeq))

```

```{r identify-met, eval = TRUE, message = FALSE, warning = FALSE}

# check library size (number of reads) in each sample, as a function of whether that sample was a true positive sample or a negative control

# The library sizes of the positive samples primarily fall from 50,000 to 100,000 reads. The negative control samples have the lowest reads as expected. Note: It is important keep the low-read samples for now, because we want to use those negative controls to help identify contaminants!

df <- as.data.frame(sample_data(physeq))
df$LibrarySize <- sample_sums(physeq)
df <- df[order(df$LibrarySize),]
df$Index <- seq(nrow(df))
ggplot(df, aes(x=Index, y=LibrarySize, color=Type)) + 
  geom_point() + 
  scale_y_continuous(breaks=c(2000, 25000, 50000, 75000, 100000, 
                              120000, 150000, 175000, 200000,
                              225000, 250000))

ggsave("18S/librarysize_samples_met.pdf", height = 4, width = 5, units = "in", dpi=300)

# Identify Contaminants - Prevalence
# Prevalence (presence/absence across samples) of each sequence feature in true positive samples is compared to the prevalence in negative controls to identify contaminants.

# In our phyloseq object, "Type" is the sample variable that holds the negative control information. 
# We’ll summarize that data as a logical variable, with TRUE for control samples, as that is the form required by isContaminant.

sample_data(physeq)$is.neg <- sample_data(physeq)$Type == "control"
contamdf.prev <- isContaminant(physeq, method="prevalence", neg="is.neg")
table(contamdf.prev$contaminant)

# This shows there are 5 potential contaminants out of 503 sequences.

list <- (which(contamdf.prev$contaminant)) # identify which lines represent contaminants
list

# the default threshold for a contaminant is 0.1. At 0.5, this indicates that contaminants are sequences that are more prevalent in negative controls than in positive samples. This is a more aggressive approach.
contamdf.prev05 <- isContaminant(physeq, method="prevalence", neg="is.neg", threshold=0.5)
table(contamdf.prev05$contaminant) 

list05 <- (which(contamdf.prev05$contaminant)) # identify which lines represent contaminants
list05

# identified 19 potential contaminants. 

#Let’s take a look at the number of times several of these taxa were observed in negative controls and positive samples.

# 0.5 threshold
physeq.nc <- prune_taxa(!contamdf.prev05$contaminant, physeq)
physeq.c <- prune_taxa(contamdf.prev05$contaminant, physeq)
physeq.control <- merge_phyloseq(physeq.nc, physeq.c)
physeq.control

contamdf.prev05.visual <- isContaminant(physeq.control, method="prevalence", neg="is.neg", threshold=0.5)
table(contamdf.prev05.visual$contaminant) 

list <- (which(contamdf.prev05.visual$contaminant)) # identify which lines represent contaminants
list

physeq.pa <- transform_sample_counts(physeq.control, function(abund) 1*(abund>0))
physeq.pa.neg <- prune_samples(sample_data(physeq.pa)$Type == "control", physeq.pa)
physeq.pa.pos <- prune_samples(sample_data(physeq.pa)$Type == "sample", physeq.pa)

# Make data.frame of prevalence in positive and negative samples
df.pa <- data.frame(pa.pos=taxa_sums(physeq.pa.pos), pa.neg=taxa_sums(physeq.pa.neg),
                    contaminant=contamdf.prev05.visual$contaminant)

ggplot(data=df.pa, aes(x=pa.neg, y=pa.pos, color=contaminant)) + geom_point() +
  xlab("Prevalence (Negative Controls)") + ylab("Prevalence (True Samples)")

ggsave("18S/contam_prevalence_tresholds_met.pdf", height = 3, width = 4, units = "in", dpi=300)

```

```{r extract-met, eval = TRUE, message = FALSE, warning = FALSE}

# now let's take a look at these contaminants and identify what they are for threshold set to 0.5
list <- (which(contamdf.prev05$contaminant))
list # this is an index of the dataframe

summary(contamdf.prev05)
class(contamdf.prev05)
head(contamdf.prev05)

# this takes the index and extracts the relevant entries that are contaminants so we can blast it.
df <- contamdf.prev05[list, ]
head(df)
summary(df)
write.csv(df, "18S/contaminants-seqs-ctd-prev05_met.csv", row.names = TRUE)

lines <- readLines("../00_qiime2-outputs/18S/prdb-metazoa-ctd-rep-seqs.fasta")
head(lines)

headers <- rownames(df) # this pulls all the sequence names
headers
headers <- paste0(">", headers) # create headers that match the fasta file
headers

# create a new fasta file with just the decontaminants
extracted_sequences <- character()

# Loop over the lines in the fasta file
for (i in 1:(length(lines) - 1)) {
  # Check if the current line is a header line
  if (substr(lines[i], 1, 1) == ">") {
    # Check if the current header is in the list of headers to extract
    if (lines[i] %in% headers) {
      # Extract the corresponding sequence
      extracted_sequences <- c(extracted_sequences, lines[i], lines[i + 1])
    }
  }
}

head(extracted_sequences)
writeLines(extracted_sequences, "18S/decontam-extracted-seqs-ctd-contaminants-prev05_met.fasta")

```

## Evaluating contaminants

After extracting the contaminants, the fasta files can be blasted to identify the top matches. I used Geneious Prime to blast the sequences. I created a new AR43-18S folder and imported the contaminants fasta files. 

```{r check-prev05-met, eval = TRUE, message = FALSE, warning = FALSE}
# check feature frequency for identified contaminants

# this file was downloaded from the prdb-metazoa-ctd-table.qzv visualization
freq <- read.csv("18S/prdb_met_feature-frequency-detail.csv")
head(freq)
# rename columns
colnames(freq);
names(freq)[1] <- "feature"
names(freq)[2] <- "frequency"

head(freq)

# read in the contamination file that was generated earlier
prev05 <- read.csv("18S/contaminants-seqs-ctd-prev05_met.csv")

# I can create a joint table that combines the two files to show feature frequency

## first, I have to rename "X" to be feature (to match the feature freauency file)
names(prev05)[1] <- "feature"
head(prev05)
prev05_df <- left_join(prev05, freq, by="feature")
head(prev05_df)
summary(prev05_df)
dim(prev05_df)

## I can also import the blast results and combine them
blast <- read.table("../00_qiime2-outputs/18S/ar43-18s-silvadb-taxonomy_hybrid_classify.tsv", sep='\t', header=T, row.names=1, comment = "")
head(blast)
colnames(blast)
head(blast)
dim(blast)
class(blast)
rownames(blast)
colnames(blast)
blast$feature <- rownames(blast)
head(blast)
colnames(blast)
blast_df <- as.data.frame(blast[c(2:12715), c(1:5)])
summary(blast_df)
head(blast_df)
join_df <- left_join(prev05_df, blast_df, by = "feature")
head(join_df)
join_df$Taxon
dim(join_df)

write.csv(join_df, "18S/met_blast-contaminants-seqs-prev05_18s_hybrid.csv", row.names = TRUE)

```

```{r decontam-met, eval = TRUE, message = FALSE, warning = FALSE}
# Now that we have identified likely contaminants, let’s remove them from the phyloseq object based on 0.5 threshold

#let's check the 0.5 threshold:
head(contamdf.prev05)
tail(contamdf.prev05)
dim(contamdf.prev05)
rownames(contamdf.prev05)

physeq
physeq.noncontam <- prune_taxa(!contamdf.prev05$contaminant, physeq)
physeq.noncontam

saveRDS(physeq.noncontam, file = "../02_phyloseq/18S/decontam-metazoa-ctd-phyloseq_05.rds") # save the file

```

